\thetitle

### 2021-03-02 writing/rational.tex
pass over section 5

Section~\ref{sec:why-rational} explains, and illustrates with an example, how a
migratory type setting helps with finding the source of an impedance
mismatch. Roughly speaking, it encourages the rational programmer to equip a
module with types if it is blamed in an error message. A sequence of such steps
make up a portion of the migratory path in the lattice of type
migration~\cite{tfgnvf-popl-2016} (see sec.~\ref{sub:stuff} for details).

Unfortunately, the rational programmer receives different kinds of information
and thus may construct different paths. As section~\ref{sec:landscape} shows,
the three different semantics deal with the same program in three different
ways, and the error messages point to different sources of a problem.

Hence the research problem is how to make the actions of a rational programmer
comparable across all semantics. Sections~\ref{sub:natural}
through~\ref{sub:erasure} describe the various rational programmers and explain
to what extent their actions are comparable. Section\ref{sub:experiment}
enhances comparability with the programmer-effort dimension. Finally, the last
subsection states the experimental questions.

>>>>

Section~\ref{sec:why-rational} explains, and illustrates with an example,
how a migratory type setting helps with finding the source of an impedance
mismatch. Roughly speaking, it encourages the rational programmer to
equip a module with types if it is blamed in an error message. A sequence
of such steps make up a portion of the migratory path in the lattice of
type migration~\cite{tfgnvf-popl-2016}. The lattice, described in Section
~\ref{sub:stuff},  serves as the common substrate for the definition modes
of the rational programmer mentioned in section~\ref{sec:challenges}.

Each mode receives different kinds of information and thus may construct
different paths in the lattice. As discussed in~\ref{sec:challenges},
evaluating blame relies on comparing modes of the rational programmer
within the same semantics and across different semantics.

Hence the research problem is how to make the actions of a rational programmer
comparable across all semantics. Sections~\ref{sub:natural}
through~\ref{sub:erasure} describe the various mode of the rational programmer and explain
to what extent they are comparable. Section\ref{sub:experiment}
enhances comparability with the programmer-effort dimension. Finally, the last
subsection states the experimental questions and gives an overview of the
experimental process.
